Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex
fix some undefined citations and other compile errors
Many:
-eliminated review_todo
-More details on why transformations are safe
-Bib fixes

\begin{figure}
\begin{verbatim}
expr = choose {
  PAREN = <uint8='('; *expr; uint8=')'>
  PRODUCT = sepBy1 uint8='*' expr
  SUM = sepBy1 uint8='+' expr
  INTEGER = many1 uint8 | '0' .. '9'
}
\end{verbatim} \cc{paren = < uint8="("; optional *paren; uint8=")" >}.
\caption{Grammar for sums and products of integers.}
\label{fig:grammar-arith}
\end{figure}
% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, f

@@

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library.

>>>>

\begin{figure}
\begin{verbatim}
expr = choose {
  PAREN = <uint8='('; *expr; uint8=')'>
  PRODUCT = sepBy1 uint8='*' expr
  SUM = sepBy1 uint8='+' expr
  INTEGER = many1 uint8 | '0' .. '9'
}
\end{verbatim}
% \cc{paren = < uint8="("; optional *paren; uint8=")" >}.
\caption{Grammar for sums and products of integers.}
\label{fig:grammar-arith}
\end{figure}
% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, f

@@

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library. 
For example, our Zip transformations are 78 lines of code, compared to 1600 lines of code for a
   hand-written parser. Additionally, Nail provides convenient and safe interfaces for allocating
   memory and accessing streams that address the most common occurences of buffer overflow
   vulnerabilities.

### 2014-09-10 paper/osdi14/impl.tex
impl.tex: fix an obvious typo pointed out by Reviewer C
Many:
-eliminated review_todo
-More details on why transformations are safe
-Bib fixes

The current prototype of the Nail parser generator supports the C programming
language. The implementation parses Nail grammars with Nail itself, using a
130-line Nail grammar feeding into a 2,000-line C++ program that
emits the parser and generator code. Bootstrapping is
performed with a subset of the grammar implemented using conventional grammars. 
And option for C++ STL data models  is in development. In
this section, we will discuss some particular features of our parser
implementation.

@@

\paragraph{Parsing.}

@@

\XXX[Add API here]
\paragraph{Defense-in-Depth.}

@@

Furthermore, the internal representation does not include any references to the input stream, which
can therefore be zeroed immediately after the parser succeeds, so an attacker has to write an
exploit that works without referencing data in the raw input.
% \paragraph{Intermediate representation.}

>>>>

The current prototype of the Nail parser generator supports the C programming
language. The implementation parses Nail grammars with Nail itself, using a
130-line Nail grammar feeding into a 2,000-line C++ program that
emits the parser and generator code. Bootstrapping is
performed with a subset of the grammar implemented using conventional grammars. 
An option for C++ STL data models is in development.
Figure~\ref{fig:dns-api} shows the API for the Nail-generated code.  In
this section, we will discuss some particular features of our parser
implementation.

@@

\begin{figure}[h]
\smaller[0.5]
% \input{code/dns-api}
\caption{API for the parser and generator Nail produces.}
\label{fig:dns-api}
\end{figure}
\paragraph{Parsing.}

@@

\paragraph{Defense-in-Depth.}

@@

Furthermore, the internal representation does not include any references to the input stream, which
can therefore be zeroed immediately after the parser succeeds, so an attacker has to write an
exploit that works without referencing data in the raw input.

Finally, Nail only supports error handling in a special debug configuration and will only print
error messages about the input to standard error. Besides complicating the parser, advanced error handling
invites programmers to attempt and fix malformed input, such as adding reasonable defaults for a
missing field. Such error-fixing not only introduces parser differential, but also might allow an
attacker to sneak inconsistent input past a parser.
% \paragraph{Intermediate representation.}
